\usefont{OT1}{bch}{b}{n} \normalfont \normalsize \textsc{University of Queensland} \\ [25pt] \horrule{0.5pt} \\[0.4cm] \huge Epistasis follow-up \\[0.3cm] \huge *** summary *** \\ \horrule{2pt} \\[0.5cm] \date{}

### 2015-02-18 investigation/docs/overview.tex
updtaes to scripts and report

>>>>

\begin{table}[ht]
\centering
\begin{tabular}{rlllll}
  \hline
probename & snp1 & snp2 & meanlambda & npairs \\ 
  \hline
ILMN\_1704730 & rs1884655 & rs10255470 & 2.88 & 10 \\ 
ILMN\_1710752 & rs2123758 & rs2786014 & 2.15 & 8 \\ 
ILMN\_1717234 & rs1157079 & rs7733671 & 4.31 & 17 \\ 
ILMN\_1720059 & rs12435486 & rs7837237 & 2.29 & 7 \\ 
ILMN\_1738784 & rs10930170 & rs12120009 & 2.24 & 6 \\ 
ILMN\_1755589 & rs11080134 & rs11169322 & 1.16 & 6 \\ 
ILMN\_1786426 & rs2839013 & rs8106959 & 5.65 & 20 \\ 
ILMN\_1804396 & rs1293455 & rs2655991 & 1.38 & 7 \\ 
ILMN\_2313158 & rs10869600 & rs13069559 & 3.15 & 15 \\ 
ILMN\_2372639 & rs17159840 & rs10059004 & 4.17 & 17 \\ 
ILMN\_3231952 & rs12947580 & rs8079215 & 2.16 & 6 \\ 
   \hline
\end{tabular}
\caption*{Mean lambda per probe, when 5 or more interactions are identified amongst the 501 pairs}
\end{table}
